Regularising Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-03-07 article.rnw
Add an R module for doing Mantel tests.
Use the species data file to get the species names in article.rnw.

<<include=FALSE>>=
	source("r/post-process.R")
	source("r/brute-post-process.R")
	source("r/coclassification-table.R")

	species_names <- c(
		"D. birchii",
		"D. pallidifrons",
		"D. pandora",
		"D. pseudoananassae",
		"D. simulans",
		"D. sulfurigaster"
	)
	species_output_order <- c(4,3,1,2,6,5)

	brute_data <- BruteData$new("output/brute.data", species_names)

>>>>

<<include=FALSE>>=
	source("r/post-process.R")
	source("r/brute-post-process.R")
	source("r/mantel-test.R")
	source("r/coclassification-table.R")

	species_dat <- read.csv("data/species.csv")
	species_output_order <- c(4,3,1,2,6,5)

	brute_data <- BruteData$new("output/brute.data", species_dat$name)
